---
title: "eply"
author: "William Michael Landau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Function `eply()`

```{r}
library(eply)
```

`eply()` applies a function over a data frame of expressions.

Begin with a function.
```{r}
.fun = example.fun
.fun
```

Then, make a data frame of expressions that return arguments to `.fun`.
```{r}
.expr = example.expr()
.expr
# str(.expr) # The expressions are actually just characters.
```

Those expressions need data.

```{r}
.with = example.with()
str(.with)
```

For each row in `.expr`, evaluate the expressions and feed the results to `.fun`.

```{r}
eply(.fun, .expr, .with)
```

You can discard `.with` if your data are in a clean global environment.

```{r}
a = 1
b = 2
eply(.fun, .expr)
```

# Function `evals()`

`evals()` evaluates a character vector of expressions.

```{r}
evals(c("1+1", "2+2", "3+3"))
evals(c("1+1", "2+2", "3+3"), .simplify = FALSE)
evals(c("subset(mtcars, cyl == a, mpg, TRUE)", "mtcars[1:2, 1:2]"), 
      .with = list(a = 4))
```

# Parallel execution

Eply does not implement any special parallel computing functionality. 
However, you can use the [`plyr`](http://seananderson.ca/2013/12/01/plyr.html)
package to parallelize `eply()` over chunks of `.expr`. See the
["Parallel processing"](http://seananderson.ca/2013/12/01/plyr.html#parallel-processing)
section of the linked guide.


# Functions `quotes()` and `unquote()`

If you want some expressions to actually be strings, use `quotes()`.

```{r}
.expr = data.frame(
  string = quotes(c("a", "b")),
  variable = c("c", "d"))
.expr
.fun = function(string, variable) paste(string, variable)
.with = list(c = "C", d = "D")
eply(.fun, .expr, .with)
```

Undo with `unquote()`.

```{r}
.expr$string = unquote(.expr$string)
.expr
```

# Function `strings()`

Turn valid expressions into strings with `strings()`.

```{r}
data.frame(
  arg1 = strings(a + b, sqrt(x) - 2), 
  arg2 = 1:2)
```

# More help

```{r}
help_eply()
```

